\textbf{Example of Abstract and AI-Generated Keywords for Summary} \\

Example of original PubMed abstract: ``Using a life course theory perspective, this qualitative descriptive study explored how Hispanic adolescent fathers view fatherhood, and how their perception of parenthood is shaped by critical life events. Hispanics are one of the largest ethnic groups, as well as one of the populations that is overrepresented in adolescent births in the United States. Despite this, Hispanic adolescent fathers are understudied and underrepresented in research. Participants were recruited from a community-based fatherhood program. Semi-structured interviews were conducted with Hispanic fathers, ages 16 years to 23 years. Participants conveyed their grief over fragmented family relationships and limited interactions with their own father. Some lived in hostile environments where they frequently experienced racism, discrimination, and neighborhood violence. The cumulative impact of these events resulted in substance use and emotional distress. Becoming a father was a sentinel event that helped resolve negative perceptions about fatherhood. Fatherhood also motivated participants towards a more productive, meaningful life.'' \\

\noindent AI-generated keywords: ``Hispanic, adolescent fathers, fatherhood, life course theory, qualitative descriptive study, critical life events, underrepresented, community-based program, semi-structured interviews, grief, family relationships, racism, discrimination, neighborhood violence, substance use, emotional distress, sentinel event, positive perceptions, meaningful life.''
