\textbf{A Full Example of High- and Low-LP-Score Variants} \\

For readability, words with an LP-score of $>$0.1 are highlighted in boldface, but part-of-speech is omitted. All items in both forms, with and without part-of-speech, can be found on our GitHub. \\

\noindent An example with a high LP-score: ``In a transgenic mouse model of melanoma, we \textbf{investigated} the effects of glutamine supplementation on tumour growth and survival under conditions of nutrient deprivation. Glutamine supplementation enhanced tumour growth, but when combined with a BRAF inhibitor, reduced tumour growth and increased survival. Metabolomic analysis revealed increased $\alpha$KG levels, \textbf{leading} to hypomethylation and H3K4me3 demethylation, promoting oncogenic pathways. Dietary intervention and \textbf{targeted} therapy \textbf{strategies} \textbf{targeting} these \textbf{epigenetic} modifications hold \textbf{promise} for melanoma treatment. \textbf{Furthermore}, \textbf{our} results \textbf{suggest} that glutamine supplementation may promote tumour growth, \textbf{potentially} through its role in $\alpha$KG synthesis, \textbf{highlighting} the \textbf{need} for \textbf{nuanced} nutritional approaches in cancer treatment.'' (100 words, LP-score:\ 12.6) \\

\noindent The following is the counterpart with a low LP-score: ``This study \textbf{employed} a transgenic mouse model of melanoma to \textbf{investigate} the effects of glutamine supplementation on tumour growth and survival under conditions of nutrient deprivation. The model was treated with a BRAF inhibitor, a common \textbf{targeted} therapy for melanoma. Metabolomic analysis revealed increased $\alpha$KG levels, \textbf{indicative} of glutamine metabolism, and associated with tumour growth and survival. Transcriptome analysis showed alterations in \textbf{epigenetic} marks, including hypomethylation and H3K4me3 modifications, in response to glutamine supplementation. These changes were correlated with activation of oncogenic pathways and improved tumour growth. Dietary intervention with glutamine also demonstrated enhanced tumour growth and survival in the model.'' (101 words, LP-score:\ 2.1) \\
