\textbf{IRB instructions} \\

``You are about to take part in a study whose goal it is to investigate language preferences. Your task will be to express a preference when presented with two choices. \\

\noindent Your participation is your free, rescindable choice. You will not be exposed to any known risks or uncertainties, there are not any known benefits, either. You can leave this study at any time, without specifying reasons.

\noindent Note:\ We do remove bad actors during the study and exclude their ratings from our analyses. For this, we collect the IP addresses -only of bad actors- and store these for about 24 hours.

\noindent We collect basic demographic information (age, gender, region, English proficiency) but your participation is anonymous and published data does not contain any identifiable information. Anonymised data will be published on Github. 

\noindent Estimated time for completion is about 15 minutes. Payment will be delivered through the recruitment platform. The exact payment amount will be based on the rate previously agreed upon via the recruitment platform.

\noindent If you any questions or concerns, contact the Principal Investigator: [PI info omitted].

\noindent [Institutional Review Board info omitted] is overseeing this research. The [omitted] is a group of people who perform official independent review of research studies before studies begin to ensure that the rights and welfare of participants are protected. If you have questions about your rights or wish to speak with someone other than the research team, you may contact: [Institutional Review Board info omitted] \\

\noindent \textit{I have read and considered the presented information. I confirm that I understand the purpose of the research. I understand that I may contact the Principal Investigator at any time and can withdraw my participation without prejudice.}

\noindent \textit{By clicking the right-arrow button, I indicate my willingness to participate in this study.}''\\
